Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
redaction of section VI

\begin{itemize}
\item step 1: features extraction.
\item step 2: scene-wise clustering step. A clustering is performed on each scene using an enhanced version of the popular K-means algorithm known as K-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. Each scene is then describe with a set of centroids.
\item step 3: Centroids similarity. The similarity between the centroids is computed using a radial basis function kernel $K^c$ as well as the local scaling method proposed in \cite{selfTuneManor2004}: \\
\begin{equation}
\begin{split}
K^c_{ij} & =exp\left( - \dfrac{\parallel x_i - x_j \parallel^2}{\sigma_{i}\sigma_{j}} \right) \\
\sigma_{i} & =\parallel x_i - x_N \parallel
\end{split}
\end{equation}

with $x_N$ the $N$'th nearest neihgbor of the centroid $x_i$. \\

@@

To compute the scene similarity based on the extracted centroids, we propose the three following strategies:

\begin{itemize}
\item \emph{closest}: the similarity between two scenes is equal to the largest similarity between their centroids.
\item \emph{averaged}: the similarity between two scenes is equal to the average of their centroids similarities.
\item \emph{weighted}: for each scene, each centroid is weighted according to the number of frames belonging to its cluster. 
\end{itemize}

To compute the  weighted similarity between two scenes by taking into account both theirs clusters weights and theirs centroids similarities, we use a variant of the Earth Moving Distance ($EMD$) adapted for non-normalized histograms known as $\widehat{EMD}$ \cite{pele2008linear} with the implementation proposed in  \cite{pele2009fast}. Considering $h_i$ and $h_j$, the histograms of the centroids weights of the scenes $s_i$ and $s_j$ respectively, the $\widehat{EMD}$ is computed as follow:

\begin{equation}
\begin{split}
\widehat{EMD}(h_i,h_j) &=( \min\limits_{f_{ij}} \sum\limits_{i,j} f_{ij}D_{ij} )  \\ 
&+ \mid \sum\limits_{i} h_i - \sum\limits_{j} h_j  \mid \alpha \max\limits_{i,j} D_{ij}
\end{split}
\end{equation}

\begin{equation*}
s.t. \quad f_{ij}\geq0\quad \sum\limits_{j} f_{ij} \leq h_{i}\quad \sum\limits_{i} f_{ij} \leq h_{j} 
\end{equation*}
\begin{equation*}
\sum\limits_{i,j}f_{ij} = \min( \sum\limits_{i} h_{i} ,\sum\limits_{j} h_{j} )
\end{equation*}

where $f_{ij}$ is the flow, and $D_{ij}$ is the ground distance. In our case, the ground distance is $D_{ij}=1-K^c_{ij}$.

To get the final similarity measure between two scenes $s_i$ and $s_j$, we use an extended Gaussian kernels $K^s$ \cite{chapelle1999support,jing2003support}.

\begin{equation*}
K^s(s_i,s_j) = exp\left( - \dfrac{\widehat{EMD}(h_i,h_j)}{A} \right) \\
\end{equation*}

with $A$ a scaling parameter, set to the mean value of the $\widehat{EMD}$. The resulting kernel is called an EMD kernel, and it has to be noted that there is no proof that such kernel is positive definite. \\

Other articles using EMD in vision \cite{zhang2007local}

>>>>

\begin{itemize}
\item step 1: features extraction.
\item step 2: scene-wise clustering step. A clustering is performed on each scene using an enhanced version of the popular K-means algorithm known as K-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. Each scene is then describe with a set of centroids.
\item step 3: Centroids similarity. The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}: \\
\begin{equation}
\begin{split}
K^c_{ij} & =exp\left( - \dfrac{\parallel c_i - c_j \parallel^2}{\sigma_{i}\sigma_{j}} \right) \\
\sigma_{i} & =\parallel c_i - c_N \parallel
\end{split}
\end{equation}

with $c_N$ the $N$'th nearest neihgbor of the centroid $c_i$. \\

@@

The scene similarity is computed based on the extracted centroids. We propose the three following strategies:

\begin{itemize}
\item \emph{closest}: the similarity between two scenes is equal to the largest similarity between their centroids.
\item \emph{averaged}: the similarity between two scenes is equal to the average of their centroids similarities.
\item \emph{weighted}: for each scene, each centroid is weighted according to the number of frames belonging to its cluster.\\
\end{itemize}

Compared to the closest or averaged approach, the  weighted similarity between two scenes takes into account both the clusters weights and the centroids similarities. To do so, each scene $s_u$ is viewed as a signature $S_u$ of $m$ clusters ($S_u=\lbrace(c_1^u,w_1^u),\ldots,(c_m^u,w_m^u)\rbrace$), with $c_i^u$ and $w_i^u$ being the centroid and the weight of the $i$th cluster of the scene $s_u$ respectively.

To compute the distance between two signatures $S_u$ and $S_v$, we use a variant version of the Earth Moving Distance ($EMD$), known as $\widehat{EMD}$ introduced in \cite{pele2008linear}. $EMD$ is a cross-bin histogram distance, widely used in computer vision (\cite{zhang2007local}), which compute the minimal cost to be paid to transform one histogram into the other. The advantage of using the $EMD$ is that it does not require bins to be aligned. The alignment problem is solved by using a ``\,ground distance\,'', being the distance between the bins representatives of the two histograms. In our case, the histograms are the weights $w$, and the bins representative the centroids $c$.\\

$\widehat{EMD}$ is a variant version of the $EMD$ adapted for non-normalized histograms. To compute the $\widehat{EMD}$, we use the implementation proposed in \cite{pele2009fast}. Given two signatures $S_u$ and $S_v$, the $\widehat{EMD}$ is computed by solving the following linear programming problem:

\begin{equation}
\begin{split}
\widehat{EMD}(S_u,S_v) &=( \min\limits_{\lbrace f_{ij}\rbrace} \sum\limits_{i,j} f_{ij}D_{ij} )  \\ 
&+ \mid \sum\limits_{i} w_i^u - \sum\limits_{j} w_j^v  \mid  \max\limits_{i,j}\lbrace  D_{ij}\rbrace
\end{split}
\end{equation}

\begin{equation*}
s.t. \quad f_{ij}\geq0 \quad \sum\limits_{j} f_{ij} \leq w_i^u \quad \sum\limits_{i} f_{ij} \leq w_j^v 
\end{equation*}

\begin{equation*}
\sum\limits_{i,j}f_{ij} = \min( \sum\limits_{i} w_i^u ,\sum\limits_{j} w_j^v )
\end{equation*}

where $f_{ij}$ is the optimal flow between the clusters weights $w_i^u$ and $w_j^v$, that is, the amount transported from the $i$th bin to the $j$th bin. $D_{ij}$ is the ground distance between the centroids $c_i^u$ and $c_j^v$, which is equal to $D_{ij}=1-K^c_{ij}$.\\

To obtain the final similarity measure between the scenes $s_u$ and $s_v$, an extended Gaussian kernels $K^s$ \cite{chapelle1999support,jing2003support} is computed:

\begin{equation*}
K_{uv}^s(s_u,s_v) = exp\left( - \dfrac{\widehat{EMD}(S_u,S_v)}{A} \right) \\
\end{equation*}

with $A$ a scaling parameter, set to the mean value of the $\widehat{EMD}$ between all the scenes. The resulting kernel $K^s$ is called an EMD kernel, and it has to be noted that there is no proof that such kernel is positive definite. \\
